---
title: 'DS 624 Fall2020: Project 2'
subtitle: 'ABC Beverae - PH Analysis'
author: 'Donny Lofland, Dennis Pong, Charlie Rosemond'
data: '11/15/2020'
output:
  html_document:  
    theme: cerulean
    highlight: pygments
    css: ./lab.css
    toc: true
    toc_float: true
  pdf_document:
    extra_dependencies: ["geometry", "multicol", "multirow", "xcolor"]
---

Source code: [https://github.com/djlofland/DATA624_F2020_Group/tree/master/](https://github.com/djlofland/DATA624_F2020_Group/tree/master/)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, include=TRUE)
```

```{r paged.print=FALSE,  include=FALSE}

# TODO: Remove unnecessary libraries once project is done

library(readxl)           # Y Read Excel Data

library(skimr)            # Y alternative to summary()
library(naniar)           # Y EDA for NA's
library(VIM)              # Y kNN impute of missing values

library(MASS)
library(forecast)
library(caret)
library(mlbench)

library(rpart.plot)
library(ggplot2)
library(ggfortify)
library(gridExtra)
library(ggcorrplot)
library(GGally)
library(corrplot)
library(RColorBrewer)
library(ggpmisc)

library(fpp2)
library(fma)
library(kableExtra)
library(e1071)
library(DataExplorer)
library(timeDate)
library(mixtools)
library(tidymodels)
library(regclass)
library(pROC)

library(tidyverse)        # TIDY packages
library(tidyr)
library(dplyr)
library(reshape2)
library(tibble)

#' Print a side-by-side Histogram and QQPlot of Residuals
#'
#' @param model A model
#' @examples
#' residPlot(myModel)
#' @return null
#' @export
residPlot <- function(model) {
  # Make sure a model was passed
  if (is.null(model)) {
    return
  }
  
  layout(matrix(c(1,1,2,3), 2, 2, byrow = TRUE))
  plot(residuals(model))
  hist(model[["residuals"]], freq = FALSE, breaks = "fd", main = "Residual Histogram",
       xlab = "Residuals",col="lightgreen")
  lines(density(model[["residuals"]], kernel = "ep"),col="blue", lwd=3)
  curve(dnorm(x,mean=mean(model[["residuals"]]), sd=sd(model[["residuals"]])), col="red", lwd=3, lty="dotted", add=T)
  qqnorm(model[["residuals"]], main = "Residual Q-Q plot")
  qqline(model[["residuals"]],col="red", lwd=3, lty="dotted")
  par(mfrow = c(1, 1))
}

#' Print a Variable Importance Plot for the provided model
#'
#' @param model The model
#' @param chart_title The Title to show on the plot
#' @examples
#' variableImportancePlot(myLinearModel, 'My Title)
#' @return null
#' @export
variableImportancePlot <- function(model=NULL, chart_title='Variable Importance Plot') {
  # Make sure a model was passed
  if (is.null(model)) {
    return
  }
  
  # use caret and gglot to print a variable importance plot
  varImp(model) %>% as.data.frame() %>% 
    ggplot(aes(x = reorder(rownames(.), desc(Overall)), y = Overall)) +
    geom_col(aes(fill = Overall)) +
    theme(panel.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.x = element_text(angle = 90)) +
    scale_fill_gradient() +
    labs(title = chart_title,
         x = "Parameter",
         y = "Relative Importance")
}


#' Print a Facet Chart of histograms
#'
#' @param df Dataset
#' @param box Facet size (rows)
#' @examples
#' histbox(my_df, 3)
#' @return null
#' @export
histbox <- function(df, box) {
    par(mfrow = box)
    ndf <- dimnames(df)[[2]]
    
    for (i in seq_along(ndf)) {
            data <- na.omit(unlist(df[, i]))
            hist(data, breaks = "fd", main = paste("Histogram of", ndf[i]),
                 xlab = ndf[i], freq = FALSE)
            lines(density(data, kernel = "ep"), col = 'red')
    }
    
    par(mfrow = c(1, 1))
}

#' Extract key performance results from a model
#'
#' @param model A linear model of interest
#' @examples
#' model_performance_extraction(my_model)
#' @return data.frame
#' @export
model_performance_extraction <- function(model=NULL) {
  # Make sure a model was passed
  if (is.null(model)) {
    return
  }
  
  data.frame("RSE" = model$sigma,
             "Adj R2" = model$adj.r.squared,
             "F-Statistic" = model$fstatistic[1])
}

#' Return a properly rounded Box Cox lambda (-n, ..., -1, -0.5, 0, 1, ..., n)
#'
#' @param series A time series
#' @examples
#' round_lambda(my_series)
#' @return new_lambda
#' @export
round_lambda <- function(series) {
  lambda <- BoxCox.lambda(series)
  
  if ((lambda > 0.25) & (lambda < 0.75)) {
    new_lambda <- 0.5
  } else if ((lambda > -0.75) & (lambda < -0.25)) {
    new_lambda <- -0.5
  } else {
    new_lambda <- round(lambda)
  }

  print(paste('lambda:', lambda, ',  rounded lambda:', new_lambda))
  
  return(new_lambda)
}

```

## Instructions

### Overview

This is role playing. I am your new boss. I am in charge of production at ABC Beverage and you are a team of data scientists reporting to me. My leadership has told me that new regulations are requiring us to understand our manufacturing process, the predictive factors and be able to report to them our predictive model of PH.

Please use the historical data set I am providing. Build and report the factors in BOTH a technical and non-technical report. I like to use Word and Excel. Please provide your non-technical report in a business friendly readable document and your predictions in an Excel readable format. The technical report should show clearly the models you tested and how you selected your final approach.

### Deliverables

Please submit both RPubs links and .rmd files or other readable formats for technical and non-technical reports. Also submit the excel file showing the prediction of your models for pH.

## Introduction

*Insert short overview of what the data contains and what we are trying to accomplish by building a model.  Discuss our overall approach and what models might be appropriate.*

## 1. Data Exploration

*Describe the size and the variables in the training data set. Consider that too much detail will cause a manager to lose interest while too little detail will make the manager consider that you aren’t doing your job. Some suggestions are given below.*

### Dataset

The dataset contains categorical, continuous and discrete features.  The data contains 32 features and 2571 instances, with 267 instances reserved for an evaluation dataset with targets removed.  The target column is `PH`.  While `PH` should be a continuous variable, of note, there are 52 distinct values (over the 2400+ rows).  Given this, possible models could include both regression and classification, or an ensemble of both.  

There are two files provided:

* **StudentData.xlsx** - dataset we will use to train our model.  Note the `PH` column will be our target we are trying to predict.
* **StudentEvaluation.xlsx** - holdout data used for evaluation.  Note the `PH` column is empty in this dataset - our model will have to be scored by an outside group with knowledge of the actual PH Values.

*Note: Both files are simple CSV format.*

```{r load_data}
# Load crime dataset
df <- read_excel('datasets/StudentData.xlsx')
df_eval <- read_excel('datasets/StudentEvaluation.xlsx')

# remove the empty PH column from the evaluation data
df_eval <- df_eval %>%
  dplyr::select(-PH)
```

Below is a list of the variables of interest in the data set:

* `Brand Code`: categorical, values: A, B, C, D
* `Carb Volume`: 
* `Fill Ounces`: 
* `PC Volume`: 
* `Carb Pressure`: 
* `Carb Temp`: 
* `PSC`: 
* `PSC Fill`: 
* `PSC CO2`: 
* `Mnf Flow`: 
* `Carb Pressure1`: 
* `Fill Pressure`: 
* `Hyd Pressure1`: 
* `Hyd Pressure2`: 
* `Hyd Pressure3`: 
* `Hyd Pressure4`: 
* `Filler Level`: 
* `Filler Speed`: 
* `Temperature`: 
* `Usage cont`: 
* `Carb Flow`: 
* `Density`: 
* `MFR`: 
* `Balling`: 
* `Pressure Vacuum`: 
* `PH`: **the TARGET we will try to predict.**
* `Bowl Setpoint`: 
* `Pressure Setpoint`: 
* `Air Pressurer`: 
* `Alch Rel`: 
* `Carb Rel`: 
* `Balling Lvl`: 

### Summary Stats

We compiled summary statistics on our dataset to better understand the data before modeling. 

```{r data_summary}
# Display summary statistics
skim(df)
```

The first observation is that we have quite a few missing data points across our features (coded as NA's) that we will want to impute. Especially note that 4 rows are missing their `PH` value.  We will need to drop these rows as they cannot be used for training.

Based on the summary statistics, it appears we have some highly skewed features with means that are far from the median indicating a skewed distribution. Some examples include the variables ... . We also see a several variables that appears to be quite imbalanced with a large number of 0 values, e.g. `Hyd Pressure1` and `Hyd Pressure2`.  We might need to impute these.

### Check Target Class Bias

If we treat `PH` as a classification problem, we need to understand any class imbalance, as this may impact predicted classification.

Our class balance is:

```{r}
hist(df$PH)
```

`PH` is normally distributed with some possible outliers on the low and high ends.  Given this distribution, a pure classification approach may be problematic as the predictions may favor pH's in the mid-range (since we have more data points).  That said, it's still possible there are boundaries such that classification adds predictive information.  Give the normal shape, a regression or possibly an ensemble with regression and classification might be more appropriate.  

### Missing Data

Before continuing, let's understand any missing data including which features are impacted and any patterns between missing values.

```{r echo=FALSE} 
# Identify missing data by Feature and display percent breakout
# missing <- colSums(df %>% sapply(is.na))
# missing_pct <- round(missing / nrow(df) * 100, 2)
# stack(sort(missing_pct, decreasing = TRUE))

# Various NA plots to inspect data
knitr::kable(miss_var_summary(df), 
             caption = 'Missing Values',
             format="html", 
             table.attr="style='width:50%;'") %>% 
  kableExtra::kable_styling()

gg_miss_var(df)
gg_miss_upset(df)
```

Notice that ~8.25% of the rows are missing the MFR field - we may need to drop this column.  As the percentage of missing values increase, imputing may have negative consequences.  The categorical column `Brand Code` is missing 4.67% of its values.  Since we don't know if this might represent another brand or actual missing data, we will create a new categorical value 'Unknown' and assign NA's to this value.  For the rest of the features, we are only missing a small percentage, so we are probably safe with imputing using a KNN approach.

### Distributions

Next, we visualize the distribution profiles for each of the predictor variables. This will help us to make a plan on which variables to include, how they might be related to each other or `PH`, and finally identify outliers or transformations that might help improve model resolution.

```{r, fig.height = 10, fig.width = 10, echo=FALSE}
# Prepare data for ggplot
gather_df <- df %>% 
  drop_na() %>%
  dplyr::select(-c(PH, `Brand Code`)) %>%
  gather(key = 'variable', value = 'value')

# Histogram plots of each variable
ggplot(gather_df) + 
  geom_histogram(aes(x=value, y = ..density..), bins=30) + 
  geom_density(aes(x=value), color='blue') +
  facet_wrap(. ~variable, scales='free', ncol=4)
```

The distribution profiles show the prevalence of kurtosis, specifically right skew in variables `Oxygen Filler`, ..., and left skew in `Filler Speed`, ... . These deviations from a traditional normal distribution can be problematic for linear regression assumptions, and thus we might need to transform the data.  Several features are discrete with limited possible values, e.g. `Pressure Setpoint`.  Furthermore, we have a number of bimodel features, see `Air Pressurer`, `Balling`, and `Balling Level`. Bimodal features in a dataset are both problematic and interesting and potentially an area of opportunity and exploration.  Bimodal data suggests that there are possibly two different groups or classes within the feature.

Bimodal features are extremely interesting in classification tasks, as they could indicate overlapping but separate distributions for each class, which could provide powerful predictive power in a model.

While we don't tackle feature engineering in this analysis, if we were performing a more in-depth analysis, we could leverage the package, `mixtools` (see R Vignette).  This package helps regress *mixed models* where data can be subdivided into subgroups. We could then add new binary features to indicate for each instance, which distribution it belongs.

Here is a quick example showing a possible mix within `Air Pressurer`:

```{r}
# Select `Air Pressurer` column and remove any missing data
df_mix <- df %>% 
  dplyr::select(`Air Pressurer`) %>%
  tidyr::drop_na()

# Calculate mixed distributions for indus
air_pressure_mix <- normalmixEM(df_mix$`Air Pressurer`, 
                            lambda = .5, 
                            mu = c(140, 148), 
                            sigma = 1, 
                            maxit=60)

# Simple plot to illustrate possible bimodal mix of groups
plot(air_pressure_mix, 
     whichplots = 2,
     density = TRUE, 
     main2 = "`Air Pressurer` Possible Distributions", 
     xlab2 = "Air Pressurer")
```

Lastly, several features have both a distribution along with a high number of values at an extreme. However, based on the feature meanings and provided information, we have no information on whether these extreme values are mistakes, data errors, or otherwise inexplicable. As such, we will need to review each and to determine whether to impute, leave as-is, or apply feature engineering.

### Boxplots

In addition to creating histogram distributions, we also elected to use box-plots to get an idea of the spread of each variable. 

```{r, fig.height = 10, fig.width = 10, echo=FALSE}
# Prepare data for ggplot
gather_df <- df %>% 
  dplyr::select(-c(PH, `Brand Code`)) %>%
  tidyr::drop_na() %>%
  gather(key = 'variable', value = 'value')

# Boxplots for each variable
gather_df %>% ggplot() + 
  geom_boxplot(aes(x=variable, y=value)) + 
  facet_wrap(. ~variable, scales='free', ncol=6)
```

The box-plots reveal outliers, however, none of them seem egregious enough to warrant imputing or removal.  Outliers should only be dropped or imputed if we have reason to believe they are errant or contain no critical information.

### Variable Plots

Finally, we generate scatter plots of each variable versus the target variable to get an idea of the relationship between them. 

```{r, fig.height = 10, fig.width = 10, echo=FALSE}
df_features <- df %>% 
  dplyr::select(-c(PH, `Brand Code`))

df_features$PH <- df$PH
df_features <- df_features %>%
  drop_na

feature_count <- ncol(df_features) - 1

# Plot scatter plots of each variable versus the target variable
# Note that we are braking these into sets of 8 features ata  time so the 
# resulting plots are more readable.
sets <- 8
batches <- (feature_count) %/% sets

for (i in 0:batches) {
  start <- i * sets + 1
  end <- start + (sets - 1)
  
  if (end > feature_count) {
    end <- feature_count
  }
  
  # print(paste(feature_count, sets, i, start, end))
  
  p <- caret::featurePlot(x=df_features[,start:end], y=df_features[,feature_count+1], plot="pairs", pch=20)
  print(p)
}
```

The plots indicate some clear relationships between our target and features, such as `PH` & `Oxygen Filter` or `PH` & `Alch Rel`.  However, we also see clear correlations between some of the features, for example `Carb Temp` & `Carb Pressure`.  Overall, although our plots indicate some interesting relationships between our variables, they also reveal some significant issues with the data. 

For instance, most of the predictor variables are skewed or non-normally distributed, and will need to be transformed. It also appears we have some missing data encoded as 0.  

### Feature-Target Correlations

With our outliers data imputed correctly, we can now build plots to quantify the correlations between our target variable and predictor variable. We will want to choose those with stronger positive or negative correlations.  Features with correlations closer to zero will probably not provide any meaningful information on explaining crime patterns.

```{r echo=FALSE}
# Show feature correlations/target by decreasing correlation
stack(sort(cor(df_features[, feature_count + 1], df_features[,1:feature_count])[,], 
           decreasing=TRUE))
```

It appears that `Bowl Setpoint`, `Filler Level`, `Carb Flow`, `Pressure Vacuum`, and `Carb Rel` have the highest correlation (positive) with `PH`, while `Mnf Flow`, `Usage cont`, `Fill Pressure`, `Pressure Setpoint`, and `Hyd Pressure3` have the strongest negative correlation with `PH`.  The other variables have a weak or slightly negative correlation, which implies they have less predictive power.

### Multicollinearity

One problem that can occur with multi-variable regression is a correlation between variables, called Multicolinearity.  A quick check is to run correlations between variables.   

```{r echo=FALSE, fig.height=8, fig.width=10}
# Calculate and plot the Multicolinearity
df_features <- df %>%
  dplyr::select(-c(`Brand Code`))
correlation = cor(df_features, use = 'pairwise.complete.obs')

corrplot(correlation, 'ellipse', type = 'lower', order = 'hclust',
         col=brewer.pal(n=8, name="RdYlBu"))
```

We can see that some variables are highly correlated with one another, such as `Balling Level` and `Carb Volume`, `Carb Rel`, `Alch Rel`, `Density`, and `Balling`, with a correlation between 0.75 and 1 When we start considering features for our models, we'll need to account for the correlations between features and avoid including pairs with strong correlations.

As a note, this dataset is challenging as many of the predictive features go hand-in-hand with other features and multicolinearity will be a problem.

### Near Zero Variance

Lastly, we want to check for any features that show near zero variance.  Features that are the same across most of the instances will add little predictive information.  

```{r}
nzv <- nearZeroVar(df, saveMetrics= TRUE)
nzv[nzv$nzv,][1:5,] %>% drop_na()
```

`Hyd Pressure1` shows little variance - we will drop this feature.

## 2. Data Preparation

To summarize our data preparation and exploration, we can distinguish our findings into a few categories below:

### Removed Fields

* `MFR` has > 8% missing values - remove this feature.
* `Hyd Pressure1` shows little variance - remove this feature.

```{r}
# Remove the fields from our training data
df_clean <- df %>%
  dplyr::select(-c(MFR, `Hyd Pressure1`))

# remove the fields from our evaluation data
df_eval_clean <- df_eval %>%
  dplyr::select(-c(MFR, `Hyd Pressure1`))
  
```

### Missing Values

* We had 4 rows with missing `PH` that need to be removed.
* Replace missing `Brand Code` with "Unknown"
* Impute remaining missing values using `kNN()` from the `VIM` package

```{r}
# drop rows with missing PH
df_clean <- df_clean %>%
  filter(!is.na(PH))

# Change Brand Code missing to 'Unknown' in our training data
brand_code <- df_clean %>%
  dplyr::select(`Brand Code`) %>%
  replace_na(list(`Brand Code` = 'Unknown'))

df_clean$`Brand Code` <- brand_code$`Brand Code`

# Change Brand Code missing to 'Unknown' in our evaluation data
brand_code <- df_eval_clean %>%
  dplyr::select(`Brand Code`) %>%
  replace_na(list(`Brand Code` = 'Unknown'))

df_eval_clean$`Brand Code` <- df_eval_clean$`Brand Code`

# There is an edge case where our Eval data might have a `Brand Code` not seen in our training set.
# If so, let's convert them to 'Unknown'.  This is appropriate since any model trained without the
# new value wouldn't be able to glean any info from it.
codes <- unique(df_clean$`Brand Code`)

df_eval_clean <- df_eval_clean %>%
  mutate(`Brand Code`  = if_else(`Brand Code` %in% codes, `Brand Code`, 'Unknown'))

# Use the kNN imputing method from VIM package to impute missing values in our training data
df_clean <- df_clean %>% 
  kNN(k=10) %>%
  dplyr::select(colnames(df_clean))

# Use the kNN imputing method from VIM package to impute missing values in our training data
df_eval_clean <- df_eval_clean %>% 
  kNN(k=10) %>%
  dplyr::select(colnames(df_eval_clean))
```

### Outliers

No outliers were removed as all values seemed reasonable. 

### Convert Categorical to Dummy

`Brand Code` is a categorical variable with values A, B, C, D and Unknown.  For modeling, we will convert this to a set of dummy columns.

```{r warning=FALSE}
# -----
# Training data - Convert our `Brand Code` column into a set of dummy variables
df_clean_dummy <- dummyVars(PH ~ `Brand Code`, data = df_clean)
dummies <- predict(df_clean_dummy, df_clean)

# Get the dummy column names
dummy_cols <- sort(colnames(dummies))

# Make sure the new dummy columns are sorted in alpha order (to make sure our columns will match the eval dataset)
dummies <- as.tibble(dummies) %>%
  dplyr::select(dummy_cols)

# remove the original categorical feature
df_clean <- df_clean %>%
  dplyr::select(-`Brand Code`)

# add the new dummy columns to our main training dataframe
df_clean <- cbind(dummies, df_clean)

# -----
# Evaluation data - Convert our `Brand Code` column into a set of dummy variables
#df_eval_clean <- dummyVars(PH ~ `Brand Code`, data = df_eval_clean)
df_eval_clean$PH <- 1
eval_dummies <- predict(df_clean_dummy, df_eval_clean)

# Edge Case - if the eval dataset is doesn't have a specific `Brand Code`
# we will be missing the necessary dummy column.  Let's check and if necessary add 
# appropriate dummy columns with all 0's.

for (c in dummy_cols) {
  if (!(c %in% colnames(eval_dummies))) {
    eval_dummies[c] <- 0
  }
}

# Now sort the eval_dummy columns so they match the training set dummies
eval_dummy_cols <- sort(colnames(eval_dummies))
eval_dummies <- as.tibble(eval_dummies) %>%
  dplyr::select(eval_dummy_cols)

# remove the original categorical feature
df_eval_clean <- df_eval_clean %>%
  dplyr::select(-c(`Brand Code`, PH))

# add the new dummy columns to our main eval dataframe
df_eval_clean <- cbind(eval_dummies, df_eval_clean)
```

### Transform non-normal variables

Finally, as mentioned earlier in our data exploration, and our findings from our histogram plots, we can see that some of our variables are highly skewed. To address this, we decided to scale, center and BoxCox transform (using caret preProcess) to make them more normally distributed.  

```{r, echo=FALSE, fig.height=14, fig.width=8, message=FALSE, warning=FALSE}
# Drop the target, PH, we don't want to transform our target, only features
df_features <- df_clean %>%
  dplyr::select(-c(PH))

# Our evaluation (hold out data), note it didn't have the PH column
df_eval_features <- df_eval_clean

# Use caret pre-processing to handle scaling, norm'ing and BoxCox transforming our training data.
# We build the caret transformation on the training data, but will use that same xform against the 
# evaluation data.
preProcValues <- preProcess(
  df_features, 
  method = c("center", "scale", "BoxCox"))

df_transformed <- predict(preProcValues, df_features)
df_transformed$PH <- df_clean$PH

df_eval_transformed <- predict(preProcValues, df_eval_features)

preProcValues
```

Here are some plots to demonstrate the changes in distributions before and after the transformations:

```{r fig.height = 10, fig.width = 10}
# Prepare data for ggplot
gather_df <- df_transformed %>% 
  dplyr::select(-c(PH)) %>%
  gather(key = 'variable', value = 'value')

# Histogram plots of each variable
ggplot(gather_df) + 
  geom_histogram(aes(x=value, y = ..density..), bins=30) + 
  geom_density(aes(x=value), color='blue') +
  facet_wrap(. ~variable, scales='free', ncol=4)
```

As expected, the dummy variables, e.g. ` ``Brand Code``A` appear are binary and we still have bimodal features as we didn't apply any feature engineering on them.  A few still show skew, e.g. `PSC Fill` and `Temperature`, but they are closer to normal. 

### Finalizing the dataset for model building 

With our transformations complete, we can now continue on to building our models.

## 3. Build Models

*Using the training data, build at least three different models.  Since we have multicolinearity, we should select appropriate models intolerate of it or do feature selection* 

*Be sure to explain how you can make inferences from the model, as well as discuss other relevant model output. Discuss the coefficients in the models, do they make sense? Are you keeping the model even though it is counter-intuitive? Why? The boss needs to know.* 

### Model-building methodology  

With a solid understanding of our dataset at this point, and with our data cleaned, we can now start to build out candidate models.  We will explore ...(LR, PLS?, KNN?, SVM?, )

*Need answer from Jeff on explanability vs Accuracy ... if accuracy, then Neural Net or t-SNE probably better direction.  Not all models have varImp() method for variable importance.*

First, we decided to split our cleaned dataset into a training and testing set (80% training, 20% testing). This was necessary as the provided holdout evaluation dataset doesn't provide `PH` values so we cannot measure our model performance against that dataset.  

```{r}
set.seed(123456)

# utilizing one dataset for all four models
training_set <- createDataPartition(df_transformed$PH, p=0.8, list=FALSE)
df_train <- df_transformed[training_set,]
df_test <- df_transformed[-training_set,]
```

#### Model #1 *(Multi-LM)*

Using our training dataset, we decided to run a binary logistic regression model that included all non-transformed features that we hadn't removed following our data cleaning process mentioned above. 

```{r}
# Model 1 - Build Multi-Linear Regression
model1_raw <- lm(PH ~ ., df_train)

# Build model 1 - only significant features (using stepAIC)
model1 <- stepAIC(model1_raw, direction = "both",
                         scope = list(upper = model1_raw, lower = ~ 1),
                         scale = 0, trace = FALSE)

# Display Model 1 Summary
(lmf_s <- summary(model1))
confint(model1)

# Display Model 1 Residual plots
residPlot(lmf_s)

# Display Variable feature importance plot
variableImportancePlot(model1, "Model 1 LM Variable Importance")

# print variable inflation factor score
print('VIF scores of predictors')

VIF(model1)
```

Applying Model 1 against our Test Data:

```{r}
# Predict df_test and calculate performance
```

*INSERT discussion here*

#### Model #2 *(PLS?, Ridge?, ENET?)*

```{r}
#model2 <- plsr(PH ~ ., data=df_train)

#summary(model2)

# print variable inflation factor score
#print('VIF scores of predictors')

#VIF(model2)
#variableImportancePlot(model2)
```

Applying Model 2 against our Test Data:

```{r}
# Predict df_test and calculate performance
```

#### Model #3? *(Neural Network - Regression)*

*Insert discussion*

```{r}
# use caret::nnet()
```

Applying Model 3 against our Test Data:

```{r}
# Predict df_test and calculate performance
```

#### Model #4? *(kNN - Classification)*

*Insert discussion*

```{r}
```

Applying Model 4 against our Test Data:

```{r}
# Predict df_test and calculate performance
```

#### Model #5? *(XGBoost - Classification?)*

*Insert discussion*

```{r}
```

Applying Model 5 against our Test Data:

```{r}
# Predict df_test and calculate performance
```

#### Model #6? *(Kera DL NN)*

*Insert discussion*

```{r}
```

Applying Model 6 against our Test Data:

```{r}
# Predict df_test and calculate performance
```

### Model Summary  

*Insert discussion and summary*

## 4. Model Selection & Analysis 

*For the model, will you use a metric such as log-likelihood, AIC, ROC curve, etc.? Using the training data set, evaluate the model based on (a) accuracy, (b) classification error rate, (c) precision, (d) sensitivity, (e) specificity, (f) F1 score, (g) AUC, and (h) confusion matrix. Make predictions using the evaluation data set.*

*Insert discussion here*

## Predictions

We apply **Model #N** to the holdout evaluation set to predict the targets for these instances. We have saved these predictions as csv in the file `eval_predictions.csv`.

Source code: [https://github.com/djlofland/DATA624_F2020_Group/tree/master/eval_predictions.csv](https://github.com/djlofland/DATA624_F2020_Group/tree/master/eval_predictions.csv)

```{r, echo=F}
predictions <- predict(model1, df_eval_transformed)
df_eval$PH <- round(predictions, 2)

write.csv(df_eval, 'eval_predictions.csv', row.names=F)
```

## References

- A Modern Approach to Regression with R: Simon Sheather
- Linear Models with R: Julian Faraway. 
- R package vignette, [mixtools: An R Package for Analyzing Finite Mixture Models](https://cran.r-project.org/web/packages/mixtools/vignettes/mixtools.pdf)
- [7 Classic OLS assumptions](https://statisticsbyjim.com/regression/ols-linear-regression-assumptions/)
- [Detecting Multicolinearity with VIF](https://online.stat.psu.edu/stat462/node/180/)
- Applied Predictive Modeling: Kuhn & Johnson

## Appendix

### R Code

```
# Copy final R code here and hide it up above
```
